Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-06 Thesis/chapter/062-post-emma.tex
results and discussion planned
minor change results
results emma first good draft
minor text

\subsection{Post-EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
Anova shows that the influence of TCal is significant as shown by the F 
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search ???
    \item KRR (???)
    \item SVM (???)
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\Gls{anova} doesn't provide a lot of extra information. 
It bestaetigt that TCal has influence on both G and phd. 
It seems that the probability of getting such data per chance that Tcal has no influence 
(null hypothesis is true) is less then 5\% (even less than 1\%). 
wrong the second is not for phd but for extended data set
but for phd even lower than 0.1 \%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{KRR}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{SVM}
\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}
\fi

>>>>

\subsection{Post-EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py
    \item grid search
    \item KRR (start with grid search) (???)
    \item SVM (start with grid search) (???)
\end{itemize}

@@

Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.

%MSE(data=all) =427
%MSE(data=emma)=250

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\Gls{anova} doesn't provide a lot of extra information. 
It bestaetigt that TCal has influence on both G and phd. 
It seems that the probability of getting such data per chance that Tcal has no influence 
(null hypothesis is true) is less then 5\% (even less than 1\%). 
wrong the second is not for phd but for extended data set
but for phd even lower than 0.1 \%
Anova shows that the influence of TCal is significant as shown by the F

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{KRR}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{SVM}
\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{PCR?}

\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Comparison} 
compare all methods. 
How should I compare them? 
What are the measurables.
